---
title: "Bioconductor_Q&A_test2"
author: "Simone Avesani, Manuel Tognon"
date: "12/14/2020"
output: html_document
---

# EX1

Which is the content of an AnnotationHub object?

a) full genomic sequence
b) efficient interface for annotation from different sources
c) set of links to annotation sources
d) transcriptomic and genomic information regarding the queried organism
e) names of the genes for the queried organism
```{r}
```

# EX2

Consider an OrgDb object. What is a keytype?

a) datatype which can be used as key
b) key value to query the object
c) type of a key
d) ENSEMBL, NCBI, etc. genes naming style
e) keytype are available for TxDb objects and are not available for OrgDb objects
```{r}
```

# EX3 

Assume a TxDb object called `txdb`. Which is the class of the resulting object when calling `transcripts(txdb)`?

a) DataFrame
b) IRanges
c) DNAStringSet
d) TxDb
e) GenomicRanges
```{r}
```

# EX4

How many chromosomal sequences are available for Homo Sapiens (hg19 genome assembly)? Use the appropriate Bioconductor
package.

a) 23
b) 24
c) 93
d) 26
e) 52
```{r}
```

# EX5

Which is Organism.dplyr package main aim?

a) deploy information regarding the queried organism(s)
b) retrieve genomic, transcriptomic and proteomic data for the queried organism(s)
c) give an efficient and simple SQL-like interface to query and map annotation data
d) give an efficient and simple annotation database to query 
e) give a simple interface to deploy computational biology algorithms on data related to the queried organism
```{r}
```


# EX6 

Using Annotationhub(), collects the unique GRanges record from UCSC dataprovider, keep only sequences with chr1 as seqlevel an print its seqlength 

```{r}
grs <- ah[which(ah$rdataclass == "GRanges" && ah$dataprovider == "UCSC"),]
gr1 <- keepSeqlevels(grs[[2]], "chr1", pruning.mode="coarse")
seqlengths(gr1)
```


# EX7

From Annotationhub retrive the number of species contained in OrgDB, extract the record from "Drosophila grimshawi" specie and check if "Cp19" is contained inside the ALIAS keytype
```{r}
orgs <- subset(ah, ah$rdataclass == "OrgDb")
orgs$species
es <- query(orgs, "Drosophila grimshawi")[[1]]
keytypes(es)
"Cp19" %in% keys(es, keytype="ALIAS")

```


# EX8

Extract the genes represented by a single genomic range (exons located only on one strand of the reference sequence) from "TxDb.Hsapiens.UCSC.hg19.knownGene", extract only the sequences with positive strand and belonging to the "chr2".
Rename the seqlevel of the genomicRange obained mapping the seqlevel to "NCBI"
```{r}
txdb <- TxDb.Hsapiens.UCSC.hg19.knownGene
g <- genes(txdb)
seqinfo(g)
positive <- g[ strand(g) == "+"]
positive <- keepSeqlevels(positive, "chr2", pruning.mode="coarse")

newStyle <- mapSeqlevels(seqlevels(positive), "NCBI")
gr <- renameSeqlevels(positive, newStyle)
```

