---
title: "Bioconductor_Q&A_test3"
author: "Simone Avesani, Manuel Tognon"
date: "1/7/2021"
output: html_document
---


# EX1

What is Summarized Experiment?

a) it is an R class to store matrices of experimental results (RNAseq, proteomics) with addiotional metadata (x)
b) it is an R class to represent a matrix storing multiple DataFrames
c) it is a Python3 class to store matrices of sperimental results (RNAseq, proteomics) with addiotional metadata
d) it is an R class to store DataFrames of experimental results (RNAseq, proteomics), with additional metadata, where 
the rows represents the genomic ranges of interests
e) it is an R class representing an array of matrices of experimental results
```{r}
```


# EX2

Which is the difference between Summarized Experiment and Ranged Summarized Experiment?

a) SummarizedExperiment can contain an unlimited number of experimental data, while RangedSummarizedExperiment can only
contain a user-defined range of experimental data
b) There is no difference between the two
c) SummarizedExperiment is a child class of RangedSummarizedExperiment
d) RangedSummarizedExperiment contains the Genomic Ranges in the rows along with the experimental data, while the 
SummarizedExperiment object does not contain Genomic Ranges (x)
e) SummarizedExperiment can contain metadata, while RangedSummarizedExperiment cannot contain metadata
```{r}
```


# EX3 

What is a Multiassay object?

a) it is an R data structure to represent and analyze transcriptomics and proteomics experiments
b) it is an R data structure to represent and analyze multi-omics experiments (x)
c) it is an R data structure to represent the metadata of a SummarizedExperiment object
d) it is an R object reprenting an array of SummarizedExperiment objects
e) it is the parent class of SummarizedExperiment class
```{r}
```


# EX4

Which is the difference between ColData and RowData in Multiassay?

a) ColData is a vector, while RowData is a DataFrame
b) ColData contains information related to experimental dat, while RowData sotores specimen metadata
c) RowData contains the matrices with experimental data, while ColData stores the sample identifiers
d) There is no difference
e) ColData stores specimen metadata, while RowData contains information related to experimental data (x)
```{r}
```


# EX5

What is a TCGA barcode?

a) it identifies cancer gene on NCBI data portal (available also through TCGA R library)
b) it is a primary identifier of biospecimen data within the TCGA project and it is composed by a single and unique 
identifier
c) it identifies the cell lines used to obtain experimental data available on TCGA data portal (available also through 
TCGA R library)
d) it is a primary identifier of biospecimen data within the TCGA project and it is composed by a collection of 
identifiers (x)
e) it is the identifier of the protein produced by the corresponding gene, when it is in a tumoral state
```{r}
```


# EX6

Import the MultiAssayExperiment ```miniACC```. Print a table to show how many patiens have complete data for all assays. 
Keep only the patients having complete data for all assays. From ```miniACC``` select only the "RNASeq2GeneNorm" assay 
and create a complete SummarizedExperiments (adding also the appropriate colData). Use as colnames the TCGAbarcode of 
the partecipants.
```{r}
```


# EX7

Consider ```airway``` dataset. How many samples are "treated" and how many are "untreated"? Which are the unique names 
of  the cell lines used in the study? Which is the publication where ```airway``` data were presented? (Hint: import airway dataset using library())
```{r}
```


# EX8

Consider ```miniACC``` dataset. How many RNA-seq counts are available, on average, for genes "MAPK14" and "IGFBP2"?
Retrieve the name of the protein produced by "IGFBP2" (Hint: all you need is available in miniACC multiassay).
```{r}
```


# EX9

Consider the dataset ```airway_new.RDS``` and ```coldata.rds```. Load them in your R workspace. 
Consider also the TSV file ```data/pathaways_scoring.tsv```. The file contains a matrix with the enrichment score of 300 
hypothetical biological pathways into the "airway_new" dataset samples. Load it into an appropriate R data structure. 
Rename the sample names using the sample IDs in "airway_new" dataset. Then, create a SummarizedExperiment with all the 
information related to the considered samples (in ```coldata.rds```). Put these information in the appropriate location 
of the SummarizedExperiment. Compute the average enrichment score by sample and than by pathway. Which are the pathways 
and samples with the highest average enrichment score? Put this information in metadata.
Map the ENSEMBL gene names to the corresponding gene symbols and put the information in the right location of the 
SummarizedExperiment. 
```{r}
```