---
title: "Bioconductor_Q&A_test2"
author: "Simone Avesani, Manuel Tognon"
date: "12/14/2020"
output: html_document
---

# EX1

Which is the content of an AnnotationHub object?

a) full genomic sequence
b) efficient interface for annotation from different sources
c) set of links to annotation sources
d) transcriptomic and genomic information regarding the queried organism
e) names of the genes for the queried organism
```{r}
```

# EX2

Consider an OrgDb object. What is a keytype?

a) datatype which can be used as key
b) key value to query the object
c) type of a key
d) ENSEMBL, NCBI, etc. genes naming style
e) keytype are available for TxDb objects and are not available for OrgDb objects
```{r}
```

# EX3 

Assume a TxDb object called `txdb`. Which is the class of the resulting object when calling `transcripts(txdb)`?

a) DataFrame
b) IRanges
c) DNAStringSet
d) TxDb
e) GenomicRanges
```{r}
```

# EX4

How many chromosomal sequences are available for Homo Sapiens (hg19 genome assembly)? Use the appropriate Bioconductor
package.

a) 23
b) 24
c) 93
d) 26
e) 52
```{r}
```

# EX5

Which is Organism.dplyr package main aim?

a) deploy information regarding the queried organism(s)
b) retrieve genomic, transcriptomic and proteomic data for the queried organism(s)
c) give an efficient and simple SQL-like interface to query and map annotation data
d) give an efficient and simple annotation database to query 
e) give a simple interface to deploy computational biology algorithms on data related to the queried organism
```{r}
```



