---
title: "Bioconductor_Q&A_test"
author: "Simone Avesani, Manuel Tognon"
date: "12/10/2020"
output: html_document
---

# EX1

What is a normal IRanges?

a) is an IRanges with values normalized between 0 and 1
b) is a minimal representation of the IRanges viewed as a set 
c) is a minimal representation of the IRanges viewed as an array
d) is a set with as much ranges from the original IRanges object as possible
e) is an array with as much ranges from the original IRanges object as possible
```{r}
```

# EX2

What is an Hits object obtained after finding the overlaps between two IRanges?

a) it is a DataFrame which describes the relationship between two IRanges
b) it is a vector containing the overlapping positions
c) it is an array containing the overlapping positions
d) it is a matrix which describes the relationship between two IRanges
e) it is a matrix which describes the position in the genome overlapping an IRanges
```{r}
```

# EX3

Which kind of strings can be represented using a BioStrings object?

a) only DNA
b) RNA and DNA
c) DNA and aminocidic sequences
d) RNA and aminoacidics sequences
e) DNA, RNA and aminoacidics sequences
```{r}
```

# EX4

What is a consensus matrix?

a) a DataFrame containing the translated DNA codons
b) an array containing the letter probabilty at each position
c) a matrix containing  the letter probability at each position
d) a DataFrame containing the letter probability at each position
e) a matrix containing the translated DNA codons
```{r}
```

# EX5

Which is the resulting object calling coverage() on a GRanges?

a) a named Rle List object with one coverage vector per seqlevel of the GRanges
b) the sequencing depth per ranges in the GRanges
c) a coverage vector between all the sequences
d) a named List object with one coverage vector per seqlvel of the Granges
e) coverage() works on Biostrings and not on GRanges
```{r}
```

# EX6

Create two IRanges objects ir1 and ir2 with random start and end positions (in the range 1:100 and make 
sure that start < end). Then, resize ir1 to a width of 10. Find the overlaps between ir1 and ir2. (Hint: use
sample())
```{r}
```

# EX7

Given the following lines of code, comment what it is happening step by step.
```{r}
plotRanges <- function(x, xlim=x, main=deparse(substitute(x)),
                       col="black",sep=0.5,...){
  height <-1
  if(is(xlim, "Ranges"))
    xlim<-c(min(start(xlim)),max(end(xlim)))
   bins<- disjointBins(IRanges(start(x), end(x)+1))
  plot.new()
  plot.window(xlim, c(0, max(bins)*(height+sep)))
  ybottom <- bins*(sep+height) -height
  rect(start(x)-0.5, ybottom, end(x)+0.5, ybottom+height, col=col,...)
  title(main)
  axis(1)
}
par(mfrow = c(2,1))


ir <- IRanges(start= c(1,3,7,9), end=c(4,4,8,10))
plotRanges(ir)
ir1 <- reduce(ir)
plotRanges(ir1) 
ir2 <- disjoin(ir)
plotRanges(ir2)
```

# EX8

Create a GRanges object gr with random start and end positions (in range 1:100), chromosome and strand 
information.  Then, count how many ranges fall in the forward strand and how many ranges have a width less 
than 10. (Hint: use sample())
```{r}
```

# EX9

Given a DNA string s in IUPAC CODE MAP, transform it in the simple DNA alphabet (A, C, G, T). Then, compute 
the reverse complement and translate it into the corresponding aminoacidic sequence. (Hint: use 
IUPAC_CODE_MAP)
```{r}
s <- "NTRKWSD"
```

# EX10

Given the GRanges gr1 and gr2, sort gr1 by seqlevel and select only certain ranges from gr1 which overlap 
with gr2.
```{r}
gr1 <- GRanges(seqnames = c("chr11", "chr5", "chr3"), IRanges(c(4, 10, 25), c(18, 15, 32)), 
                           strand=c("-", "+", "+"))
gr2 <- GRanges(seqnames = c("chr11", "chr5", "chr3"), IRanges(c(7, 16, 29), c(21, 31, 31)), 
                           strand=c("-", "+", "+"))

```

# EX11

Create a random DNAString of length 100 using IUPAC symbols. Compute the reverse complement of the string and
translate it in the corresponding aminoacidic sequence. Count how many times the pattern "KR" appears in the 
aminoacidic sequence. 
```{r}
```

# EX12

Given an IRanges ir, get the flanking ranges of width 10, both on the right and on the left. Create a GRanges
gr from ir and shift it on the right by 7 positions. Then, resize it to a width of 15 with the range end fixed.
```{r}
ir <- IRanges(start = c(1, 8, 4, 10), width = c(34, 41, 98, 62), 
              names = c(paste("seq", 1:4, sep="")))
```

# EX13

Given two IRanges objects ir1 and ir2 find the overlaps between them. Comment the result. Then, create 
another IRanges object named ir3 containing the overlapping range between the first query and the first 
subject.
```{r}
ir1 <- IRanges(start = c(1, 8, 4, 10), width = c(34, 41, 98, 62), 
              names = c(paste("seq", 1:4, sep="")))
ir2 <- IRanges(start = c(30, -48, 99, 50), width = c(76, 7, 116, 67), 
              names = c(paste("seq", 1:4, sep="")))
```

# EX14

Create four random DNAStrings using IUPAC symbols. Store them in a DNAStringSet object. Then, get the letter frequency. How many codons can be obtained from the strings in the DNAStringSet?
```{r}
```

# EX15

Given a GRanges gr, keep only ranges falling in standard chromosomes. Map the seqlevels to NCBI style names.
Keep 
only data related to chromosome 11. Then add a random score (in range -10:10) to gr as metadat

```{r}
gr <- GRanges(seqnames = c("chr11", "c5hrU34", "chr5", "chr11"), IRanges(c(4, 2, 10, 25), c(18, 17, 15, 32)),
              strand=c("-", "-", "+", "+"))
```


